---
title: 'Product Management Report: ProdPad'
author: "Neil Chalk"
date: "7/30/2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Product Progress

This is the data in ProdPad current at time of report generation on `r format(Sys.Date(), "%d/%m/%Y", tz = "")`. The goals listed should match goals from the business plan for the current period. The current state of the backlog is as follows:

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(knitr)

#Replace with your own states and workflow order
states <- c("New Idea", "In Analysis", "Product Definition", 
            "Market Validation", "Queued for Dev", "In Development", "QA", "Released")


backlog <- read_csv("data-out/backlog.csv") 
backlog$workflow.status <- factor(backlog$workflow.status, levels = states, ordered = TRUE)

backlog %>% 
  group_by(.data$workflow.status) %>%
  summarise(Engagement = sum(.data$isGoal1), Revenue = sum(.data$isGoal2), Usability = sum(.data$isGoal3), Total = n()) %>%
  kable
  
backlog %>% 
  summarise(Totals = "", Engagement = sum(.data$isGoal1), Revenue = sum(.data$isGoal2), Usability = sum(.data$isGoal3), Total = n()) %>%
  kable  
  
```

Things that have been worked on in the past 3 months are:

```{r echo=FALSE}
backlog %>% 
  filter(backlog$created_at > '2018-04-28' | backlog$updated_at > '2018-04-28') %>%
  group_by(.data$workflow.status) %>%
  summarise(Engagement = sum(.data$isGoal1), Revenue = sum(.data$isGoal2), Usability = sum(.data$isGoal3), Total = n()) %>%
  kable
  
backlog %>% 
  filter(backlog$created_at > '2018-04-28' | backlog$updated_at > '2018-04-28') %>%
  summarise(Totals = "", Engagement = sum(.data$isGoal1), Revenue = sum(.data$isGoal2), Usability = sum(.data$isGoal3), Total = n()) %>%
  kable  
  
```

Items that are in the packaging phase are:

```{r echo=FALSE}
backlog %>% 
  filter(.data$workflow.status == "QA" | .data$workflow.status ==   "Released") %>%
  select(.data$title, .data$web_url, .data$workflow.status) %>%
  kable
  
```

## Feedback

This section tries to expolre insight from feedback trends. The following sources of feedback are being considered in this period:


```{r echo=FALSE, message=FALSE, warning=FALSE}
library("tm")
library("wordcloud")
library("slam")
#library("topicmodels")
library("readr")

dataset <- read_csv("data-out/feedback.csv") 

dataset %>%
  filter(dataset$created_at > '2018-04-28' | dataset$updated_at > '2018-04-28') %>%
  group_by(.data$customer.name) %>%
  summarise(Total = n()) %>% 
  arrange(desc(.data$Total)) %>%
  kable
  
```
A high-level word cloud showing the popular words contain in the feedback:

```{r echo=FALSE, message=FALSE, warning=FALSE}
feedback.data <- dataset$feedback

#Clean Text to do some data mining
feedback.data = gsub("http[^[:blank:]]+", "", feedback.data)
feedback.data = gsub("@\\w+", "", feedback.data)
feedback.data = gsub("[ \t]{2,}", "", feedback.data)
feedback.data = gsub("^\\s+|\\s+$", "", feedback.data)
feedback.data <- gsub('\\d+', '', feedback.data)
feedback.data = gsub("[[:punct:]]", " ", feedback.data)

corpus = Corpus(VectorSource(feedback.data))
corpus = tm_map(corpus,removePunctuation)
corpus = tm_map(corpus,stripWhitespace)
corpus = tm_map(corpus,tolower)
corpus = tm_map(corpus,removeWords,stopwords("english"))
tdm = DocumentTermMatrix(corpus) # Creating a Term document Matrix

m <- as.matrix(tdm$dimnames$Terms)
v <- as.matrix(tdm)
# calculate the frequency of words and sort it by frequency
word.freq <- sort(rowSums(v), decreasing = T)
wordcloud(words = m[word.freq], freq = word.freq, min.freq = 3,
          random.order = F)

```

Topic association of words found in the feedback with themes from roadmap for further investigation:
```{r echo=FALSE, message=FALSE, warning=FALSE}

#put your own terms here
findAssocs(tdm, "sign-up", 0.25)
findAssocs(tdm, "search", 0.25)
findAssocs(tdm, "feed", 0.6)
findAssocs(tdm, "API", 0.25)

```
