---
title: "Google Analytics Stats"
author: "Neil Chalk"
date: "6 November 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
# Welcome

Welcome to the Google Analytics report template based on [Google Analytics y R. Parte II: gráficos con ggplot2](http://omargonzalesdiaz.com/blog/googleanalytics-ggplot2.html) by [Omar Gonzáles Díaz](https://twitter.com/o_gonzales)  with additional work by Neil Chalk. This is part of a project aiming to show you how to use R for Product Management.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library(dplyr)
library(ggplot2)

sessions <- read_csv("data/sessions.csv")
sessions_per_hour <- read_csv("data/sessions_per_hour.csv")

heat_scale <- c("Grey","Blue","Orange","Red")
days_of_week <- c("Monday","Tuesday","Wednesday","Thursday", "Friday", "Saturday","Sunday")

sessions$medium <- trimws(sessions$medium, which = "both")
sessions$source <- trimws(sessions$source, which = "both")

#########################################

sessions$mes <- months(sessions$date)
sessions$mes <- factor(sessions$mes, levels = c("January", "February",
                                                "March", "April",
                                                "May", "June",
                                                "July", "August",
                                                "September", "October", "November", "December"), ordered = T)

sessions$dia <- weekdays(sessions$date)
sessions$dia <- ordered(sessions$dia, levels=rev(days_of_week)) 
sessions_per_hour$dia <- weekdays(sessions_per_hour$date)
sessions_per_hour$dia <- ordered(sessions_per_hour$dia, levels=rev(days_of_week)) 


sessions_per_month <- sessions %>%
  group_by(mes) %>%
  summarise(sessions = sum(sessions))

sessions_hour <- sessions_per_hour %>%
  group_by(dia, hour) %>%
  summarise(sessions = sum(sessions))

sessions_per_day <- sessions %>%
  group_by(date) %>%
  summarise(sessions = sum(sessions))
```

## Sessions 

The basic stat for how your site is performing. How many sessions do we get per month?

```{r fig.height=7, fig.width=15,echo=FALSE}

title <- "Sessions per Month" 

dd <- ggplot(sessions_per_month, aes(x = mes, y = sessions, fill = sessions, label = sessions)) 
dd <- dd +  geom_col()
dd <- dd + labs(x="Month", y="Sessions", title= title)
dd <- dd + scale_fill_gradientn(colours = heat_scale)
dd <- dd + theme(plot.title=element_text(hjust=0.1))
dd <- dd + theme(axis.ticks=element_blank())
dd <- dd + theme(axis.text=element_text(size=12))
dd <- dd + theme(legend.title=element_text(size=10))
dd <- dd + theme(legend.text=element_text(size=8))
dd <- dd + geom_label(vjust = -0.5)
dd <- dd + ylim(0,ceiling(max(sessions_per_month$sessions))+400)
dd <- dd + geom_label(fill = "white", vjust = -0.5)
dd
```


During this time, this is how the usage varies during the day over the course of a week.

```{r fig.height=5, fig.width=10,echo=FALSE}

gg <- ggplot(sessions_hour, aes(x=hour, y=dia, fill=sessions))
gg <- gg + scale_fill_gradientn(colours = heat_scale)
gg <- gg + geom_tile(color="white", size=0.1)
gg <- gg + coord_equal()
gg <- gg + labs(x=NULL, y=NULL, title="Sessions per day and hour")
gg <- gg + theme(plot.title=element_text(hjust=0.1))
gg <- gg + theme(axis.ticks=element_blank())
gg <- gg + theme(axis.text.y =element_text(size=12))
gg <- gg + theme(axis.text.x =element_text(size=10))
gg <- gg + theme(legend.title=element_text(size=10))
gg <- gg + theme(legend.text=element_text(size=8))
gg

```

What usage pattern do we predict for next week? This can be a useful question to ask if you are putting a feature in production that you expect to increase user sessions. Using a forecast algorithm like the Holt-Winters method will take into account peaks and troughs to give you a better picture of whether your change has made an impact.

```{r fig.height=5, fig.width=10,echo=FALSE}
library(forecast)
xxxx <- ts(sessions_per_day$sessions, frequency = 7)
hw(xxxx,6)
plot(hw(xxxx, 6), main = "User sessions forecast for following week", xlab ="Week number", ylab = "Sessions")


```

Who has been our main referer? How has the source of traffic changed over time?

```{r fig.height=10, fig.width=10,echo=FALSE}

sessions_fuente <- sessions %>%
  group_by(mes, source) %>%
  summarise(sessions = sum(sessions))


ee <- ggplot(sessions_fuente, aes(x = source, y = sessions, fill = sessions,
                                  label = sessions)) 
ee <- ee +  geom_col()
ee <- ee + facet_wrap(~ mes) 
ee <- ee + coord_flip()
ee <- ee + labs(x="month", y="sessions", title="sessions per month")
ee <- ee + scale_fill_gradientn(colors = c("blue", "purple", "red", "yellow"))
ee <- ee + theme(plot.title=element_text(hjust=0.1))
ee <- ee + theme(axis.ticks=element_blank())
ee <- ee + theme(axis.text=element_text(size=12))
ee <- ee + theme(legend.title=element_text(size=10))
ee <- ee + theme(legend.text=element_text(size=8))
ee <- ee +  geom_label(hjust = -0.5, color = "white")
ee

```
